---
title: "Analysing Equities"
author: "Robert W. Walker"
bibliography: "bibliography.bib"
nocite: |
     @*
params:
  ticker: "F"
format: 
   html:
     self-contained: true
     self-contained-math: true
     code-fold: true
     code-copy: hover
     code-block-border-left: true
     df-print: paged
     embed-resources: true
     fig-format: retina
     footnotes-hover: true
     html-math-method: katex
     mainfont: Playfair Display
     toc: true
     toc-title: Navigation
     theme: simplex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, message=FALSE, warning=FALSE)
```

```{r include = FALSE}
library(tidyquant)
library(ggplot2)
library(fpp3)
```

# `r params$ticker`

The [tidyquant](https://cran.r-project.org/web/packages/tidyquant/index.html) package provides tools and data for visualizing and analysing equities. Here is an example using data from `r toString(params$ticker)`.

```{r}
dat <- tq_get(toString(params$ticker))
dat %>% ggplot(aes(x = date, y = close)) +
    geom_barchart(aes(open = open, high = high, low = low, close = close)) +
    labs(title = paste(params$ticker,"Bar Chart"), y = "Closing Price", x = "") +
    theme_tq()
```

Or functions of the data, like returns.

```{r}
dat.new <- dat %>% tq_transmute(select= adjusted,
                 mutate_fun = periodReturn,
                 period     = "daily",
                 col_rename = "Ra") %>% as_tsibble(index=date) 
dat.new %>% autoplot()
```

## Adding Some Interactives

The following are a few quick interactive plots.

```{r}
library(tidyquant)
library(tidyverse)
library(magrittr)
# Use tidyquant to get the data
# Slice off the most recent 120 days
dat.tail <- tail(dat, 120)
dat.tail %<>% mutate(
    open = round(open, digits=2),
    close = round(close, digits=2),
    high = round(high, digits=2),
    low = round(low, digits=2),
    adjusted = round(adjusted, digits=2)
    )
```

Let's have a look at the data.

```{r}
library(DT)
datatable(dat.tail)
```

## The Plot

There are a few charts specifically designed for OHLC data that are included in `plotly`.  Here I want to deploy a basic one with one modification.  I want daily increases in black and daily decreases in red.

```{r}
library(plotly)
# basic example of ohlc charts
# custom colors
i <- list(line = list(color = '#000000')) # black
d <- list(line = list(color = '#FF0000')) # red
# Create the figure
fig.2 <- dat.tail %>%
  plot_ly(x = ~date, type="ohlc",
          open = ~open, close = ~close,
          high = ~high, low = ~low,
          increasing = i, decreasing = d)
fig.2
```

## `ggplot` candlestick

```{r}
dat %>%
    ggplot(aes(x = date, y = close)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
    labs(title = paste0(params$ticker," Candlestick Chart", sep=""), y = "Closing Price", x = "") +
    theme_tq()
```

## Another Plot

```{r}
dat %>%
    ggplot(aes(x = date, y = close)) +
    geom_barchart(aes(open = open, high = high, low = low, close = close)) +
    geom_ma(ma_fun = EMA, n = 50, wilder = TRUE, linetype = 5, size = 1.25) +
    geom_ma(ma_fun = EMA, n = 200, wilder = TRUE, color = "red", size = 1.25) + 
    labs(title = paste0(dat$symbol," Bar Chart", sep=""), 
         subtitle = "50 and 200-Day EMA", 
         y = "Closing Price", x = "") + 
    coord_x_date() +
    theme_tq()
```

